\documentclass[letterpaper,9pt]{extarticle}
\usepackage[letterpaper, portrait, margin=0.5in]{geometry}
\usepackage{fontspec}
\usepackage{inter}
\usepackage{hyperref}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{titlesec}
% \usepackage[none]{hyphenat}
\defaultfontfeatures{Mapping=tex-text}
\setmainfont{Inter}
\hypersetup{colorlinks,breaklinks}
\titleformat{\section}
{\color{RedViolet}\normalfont\Large\bfseries}
{\color{RedViolet}\thesection}{1em}{}

\begin{document}
    \pagestyle{empty}
    \raggedright%
    \section*{Emil Sayahi}
    \small
    Oxford, OH |
    \href{tel:+1-513-484-0972}{\color{black}{+1 (513) 484-0972}}
    |
    \href{mailto:limesayahi@gmail.com}{\color{black}limesayahi@gmail.com}\\
    \normalsize

    \raggedright%
    \begin{minipage}[t]{0.60\textwidth}
        \section*{Experience}
        \subsection*{Technology Consulting Intern}
        \subsubsection*{Protiviti}
        Remote (May 2024 - August 2024)\\
        \begin{itemize}
            \item Assisted in business platform transformation (BPT) project for a client in the automotive industry.
            \item Developed SAP BusinessObjects reports and universes in Web Intelligence and Information Design Tool.
            \item Wrote Python script to create client deliverables for the project.
        \end{itemize}

        \subsection*{Software Engineer Intern}
        \subsubsection*{HCLSoftware}
        Remote (May 2023 - August 2023)\\
        \begin{itemize}
            \item Backend and frontend development on core team for IBM UrbanCode Velocity \& HCL Accelerate.
            \item Contributed to migration of Docker Compose V1 to V2 for microservices.
            \item Designed and implemented customer-facing UI in React for major release item.
        \end{itemize}

        \subsection*{Teaching Assistant}
        \subsubsection*{Miami University}
        Oxford, OH (August 2022 - December 2023)\\
        \begin{itemize}
            \item Assisted in Systems I and Fundamentals of Programming courses.
            \item Assisted students in lab sessions, held office hours, and graded assignments.
            \item Material included C++, Java, networking, computer architecture, and relational databases.
        \end{itemize}

        \subsection*{Software Engineer Intern}
        \subsubsection*{Miami University}
        Oxford, OH (May 2022 - May 2024)
        \begin{itemize}
            \item Automating IT Service Management (ITSM) practices using Amazon RDS, MySQL, Python, and TeamDynamix iPaaS.
            \item Data integration projects included synchronising data between FM:Interact and TeamDynamix.
            \item Developed an automated assistant using GPT-4 to handle support requests using the university knowledge base.
        \end{itemize}

        \section*{Projects}
        \subsection*{Oku}
        \subsubsection*{Creator}
        Recipient of an NLnet grant through  

        % \subsection*{GTK}
        % \subsubsection*{Contributor}
        % Wrote a CI/CD pipeline for the GTK-rs project to automate maintainence of Rust language bindings for GTK\@.

        % \subsection*{tdxlib}
        % \subsubsection*{Contributor}
        % Extended the Python library for the TeamDynamix API to include additional functionality, such as retrieving reports.
    \end{minipage} 
    \hfill
    \raggedleft%
    \begin{minipage}[t]{0.3\textwidth}
        \section*{Education}
        \subsection*{Bachelor of Science (BS), Computer Science}
        Miami University, Oxford, OH (August 2021 - May 2024)\\
        GPA\@: 3.81\\

        \section*{Skills}
        \subsection*{Languages}
        Rust, C\#, Java, JavaScript, C++, R, Python, D, SQL, HTML, CSS\\
        \subsection*{Technologies}
        GTK, .NET, React, Apollo GraphQL, Docker, Kubernetes, MongoDB, MySQL, GitHub Workflows\\

        \section*{Presentations}
        \subsubsection*{Introduction to Quantum Machine Learning}
        Miami University, Oxford, OH (November 2023)\\
        Talk given at the Miami University Physics Department seminar on introductory concepts surrounding quantum computing, machine learning, and the intersection of the two fields.\\
        \subsubsection*{Automation in IT Service Management}
        Wright State University, Dayton, OH (May 2023)\\
        Talk given at the 2023 Ohio Higher Education Computing Council (OHECC) conference detailing strategies to automate ITSM practices in higher education institutions.
    \end{minipage}
\end{document}